the rethinking way of doing the binary outcome modeling

### 2021-03-24 scripts/54_rethinking_binary.Rmd
good I even got some work done after back

>>>>

```{r}
# combine M and P
low_all <- tibble(
  value = c(post_cr %>% pluck('m') %>% pluck(1), post_cr %>% pluck('p') %>% pluck(1))
) %>% mutate(grp = 'low')

high_all <- tibble(
  value = c(post_cr %>% pluck('m') %>% pluck(2), post_cr %>% pluck('p') %>% pluck(2))
) %>% mutate(grp = 'high')

cr_all <- bind_rows(
  low_all,
  high_all
)

cr_all  %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white',
                  xlab = 'Predicted probability of CR d100', ylab = 'Probability density',
                  title = '') +
      scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  ggsave('../figs/bayesican_cr_combined.pdf', width = 6, height = 4)
```
